%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
	
	%------------------------------------------------
	
	\cventry
	{Software engineer} % Job title
	{Lyft Inc} % Organization
	{San Francisco, CA, US} % Location
	{Mar. 2018 - Present} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Contributor to \href{https://support.lyftbusiness.com/hc/en-us/articles/360018624554}{"Lyft Concierge"\space\faExternalLink}, a Lyft Business product.}
			\begin{itemize}
				\item {Drove major feature development in Concierge Web and Concierge API, serving as Lead Frontend since Jan 2020.}
				\begin{itemize}
					\item {Contributed to revamp Concierge Web from a \href{https://techcrunch.com/2018/01/16/lyft-opens-up-concierge-its-ride-booking-service-for-businesses-to-all/}{UI\space\faExternalLink\space focused} to serve the needs of a limited number of partners to a product able to the evolving needs of healthcare providers (Concierge's main target market)}.
					\item {Impelled adoption of Frontend E2E testing on Concierge Web that allowed early detection of bad Web \& API deploys, reducing the burden in on-call shifts, demonstrating the worth of investing in QA, and eventually led to transferring a dedicated QE to the team.}
					\item{Led Frontend effort to enhance the Concierge's Rider experience that unblocked a new scheduled ride mode, which ultimately reduced no-show rate and support calls to Lyft's partners.}
					\item {Implemented different urgent adaptations in Concierge UI as part of COVID-19 response initiatives that were top company priorities like \href{https://support.lyftbusiness.com/hc/en-us/articles/360046169254}{Lyft Essential Deliveries \space\faExternalLink, and Health Safety commitment pledge.}}
				\end{itemize}
				\item{Promoted and supported different infra upgrades on other Frontend services across Lyft Business, like AngularJS to React, Frontend E2E testing, Kubernetes, JS to TS, Node 10 to 12, and other Frontend tooling.}
			\end{itemize}
		\end{cvitems}
	}
		
	%------------------------------------------------
	
	\cventry
	{Systems Engineer} % Job title
	{Global HITSS - consulting to Herbalife Nutrition de Mexico} % Organization
	{Guadajara, Jalisco, MX} % Location
	{Jul. 2017 - Feb. 2018} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Collaboration on a project to build new modules for the CRM software suite in the Member Technology Strategy (MTS) division.}
			\begin{itemize}
				\item {Analyze business requirements and write the technical specifications for new software modules.}
				\item {Write the release documentation of the developed software modules \& features.}
				\item {Design of the test automation tooling and its implementation on the new software components to ensure technical acceptance compliance.}
			\end{itemize}
		\end{cvitems}
	}
	

%------------------------------------------------

\cventry
{Systems Engineer} % Job title
{Ingeniería Aplicada OnePro S.A. de C.V. - consulting to Compañía Mexicana de Exploraciones S.A. de C.V.} % Organization
{Villahermosa, Tabasco, MX} % Location
{Mar. 2016 - Jul. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Collaboration in the development of a web-based system for data modeling the daily oil \& gas distribution for PEMEX's exploration and production (E\&P).}
		\begin{itemize}
			\item {Analyze the pre-existing data model from different institutional data sources, production reports, and physical archives.}
			\item {Design the new data model and the implementation of the resulting algorithm for the distribution calculation, including a task scheduler for running the algorithm in a non-blocking way and returning the results to the graphics user interface (GUI).}
			\item {Implementation of functional unit tests for the distribution calculation, which allowed to detect errors in the business logic.}
			% \item {Design and implementation of proofs-of-concept to building a more scalable architecture taking advantage of different scientific libraries for improving the new algorithm.}
		\end{itemize}
	\end{cvitems}
}

%------------------------------------------------    

\cventry
{Systems Engineer} % Job title
{Pemwork SAPI de C.V. - consulting to Compañía Mexicana de Exploraciones S.A. de C.V.} % Organization
{Villahermosa, Tabasco, MX} % Location
{Apr. 2015 - Mar. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item{Collaboration in the development of a web-based system for the management of industrial measurement instrumentation for PEMEX's E\&P.}
		\begin{itemize}
			\item{Design and implementation of the GUI skeleton using modern front-end frameworks and DevExpress controls.}
			\item{Development of custom controls for capturing complex data input like industrial calibration reports.}
			% \item{Customization of DevExpress' DocumentViewer for improving the usability of the pagination.}
		\end{itemize}		
		\item{Collaboration in the development of a web-based system for Business Process Management (BPM) for PEMEX's E\&P.}
		\begin{itemize}
			\item{Assessment and selection of a library for drawing web-based BPM diagrams according to the following criteria: extensibility, documentation (and community size \& activity for open source libraries), and the compliance with the BPMN 2.0 standard.}
			\item{Custom implementation of selected library (modeler \& viewer), extending it to add the required features by the project.}
			% \item{Research and development of a proof-of-concept for the integration of Kendo controls with Angular.}
		\end{itemize}
	\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Engineer} % Job title
{Compañía Mexicana de Exploraciones S.A. de C.V.} % Organization
{Villahermosa, Tabasco, MX} % Location
{Sep. 2014 - Apr. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Collaboration in a project for the migration of an ASP.Net Web forms app to ASP.Net MVC 4 web app.}
		\begin{itemize}
			\item {Migration of ASPX Views to MVC Razor Views, replacing WebForms controls with DevExpress controls.}
			\item {Development of an extension for Visual Studio 2013 for implementing a custom MVC 4 Scafoldding compatible with Entity Framework 5 and integrating DevExpress controls in the Views.}
			\item {Implementation of a role-based access control by developing a custom AuthorizeAttribute for MVC 4. }
			\item {Development of a custom theme assembly for DevExpress to match the controls' appearance with the application design.}
		\end{itemize}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Grupo Empresarial Syfors S.A. de C.V.} % Organization
{Saltillo, Coahuila, MX} % Location
{Sep. 2013 - May 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Implementation of Wordpress-based sites. Development and customization of plugins and themes.}
		\item {Development of a web-based ERP system for sales, delivery, and warehouse management, involved in activities like:}
		\begin{itemize}
			\item {Development of backend with PHP/MySQL (Codeigniter, PHPExcel) over a load balanced network of VPS servers with Ubuntu.}
			\item {Implementation of responsive frontend with Bootstrap, jQuery (and multiple jQuery-based libraries), DataTablesJS, jQuery BBQ (to make it work as a single-page app), HTML5 (LocalStorage and Geolocation) and Google Maps API v3.}
			\item {Development of a Java applet as an interface for printing receipts directly to Point of Sale printers from the web browser.}
			\item {Implementation of a heuristic algorithm for the quasi-live optimization of delivery routes based on time/distance data retrieved from Google Maps API.}
			\item {Development of an Android app for displaying the app and access to hardware API in mobile devices with a ChromeWebView.}
		\end{itemize}
	\end{cvitems} 
}

%------------------------------------------------

\cventry
{Freelance Software Engineer} % Job title
{Freelancer.com - (\href{https://freelancer.com/u/DraKkareS.html}{https://freelancer.com/u/DraKkareS.html})} % Organization
{Remote} % Location
{Oct. 2008 - Feb 2015 (Occasional)} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {150+ successful small and mid-size projects with clients from diverse nationalities, involving technologies like:
		\begin{itemize}
			\item {Dynamic web apps with PHP/MySQL (frameworks: CodeIgniter, Slim, PhalconPHP)}
			\item {HTML5, CSS3, Responsive CSS3 w/Bootstrap, OOP Javascript, jQuery, jQueryUI.}
			\item {Desktop applications with C\#.}
			\item {Google App Engine apps in Python.}
			\item {Set up and deployment of apps to linux-based servers in Atlantic.net and DigitalOcean.}
			\item {Wordpress plugins and themes.}
			\item {Scripts for Bash shell, Perl and Python.}
			\item {Scripts for data scraping with PHP/cURL, Python/Scrapy \& with C\# using TCP sockets, and Regular Expressions for data parsing.}
		\end{itemize}	
	}	
	\end{cvitems}
}

%------------------------------------------------

\end{cventries}