%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Side projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{d3-polytree (developer)} % Affiliation/role
{Interactive D3.js-based visualization of directed acyclic node networks.} % Organization/group
{ } % Location
{github:davcs86/d3-polytree} % Date(s)
{ % Description(s) of experience/contributions/knowledge
	\begin{cvitems}
		\item {Built from scratch as a NPM package (for v1) and as a modular NPM package (for v2, see branch \#new-arch-webpack).}
		\item {Improvement of the bundling process by replacing Grunt (for v1) with Webpack (for v2).}
		\item {Implementation of a D3.js based Viewer (for v1), and a D3.js v4 based Editor/Modeler (for v2).}
		\item {Outcome: Gained experience in working with D3.js and building from scratch modular NPM packages.}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{BPMN-js library (contributor \& community member)} % Affiliation/role
{A BPMN 2.0 rendering toolkit and web modeler.} % Organization/group
{ } % Location
{github:bpmn-io/bpmn-js} % Date(s)
{ % Description(s) of experience/contributions/knowledge
	\begin{cvitems}
		\item {Contributed by adding multi-language support to the base class (diagram-js).}
		\item {Contributed with the support for multiple extensions of the BPMN 2.0 standard without building a custom bundle.}
		\item {Development and shared with the community, a module to integrate Angular's i18Next with the multi-language support.}
		\item {Shared with the community, an example of a custom implementation of the library in an Angular environment.}
		\item {Outcomes: Learned the architecture of a real-world modular NPM package, unit testing in javascript with Karma.}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{Highcharts4Net (developer)} % Affiliation/role
{ASP.Net MVC5 HTMLHelpers for Highcharts 1.7.} % Organization/group
{ } % Location
{github:davcs86/Highcharts4Net} % Date(s)
{ % Description(s) of experience/contributions/knowledge
	\begin{cvitems}
		\item {Built as fork of DotNet.Highcharts, refactored to work as a custom HTMLHelper for ASP.Net MVC5 razor views.}
		\item {Refactoring the code to improve the inheritance and polymorphism in the classes.}
		\item {Improvement of the JSON serialization by replacing Newtonsoft.Json with a custom version of FastJSON.}
		\item {Outcomes: Consolidated experience in working with generic typed classes, learned stronger OOP concepts and delegates in .Net.}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{ConektaClient (developer)} % Affiliation/role
{A .Net client for Conekta.io payments platform API.} % Organization/group
{ } % Location
{github:davcs86/conekta-csharpnet} % Date(s)
{ % Description(s) of experience/contributions/knowledge
	\begin{cvitems}
		\item {Built, inspired by the Java version, to consume the Conekta's REST API using HttpWebRequest.}
		\item {Implementation of the dynamic serialization and deserialization of JSON using Newtonsoft.Json.}
		\item {Outcome: Experience in working with generic typed classes in .Net.}
	\end{cvitems}
}

\end{cventries}