%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Full-stack web developer \& .Net/Python developer} % Job title
{Ingeniería Aplicada OnePro S.A. de C.V. - consulting to Compañía Mexicana de Exploraciones S.A. de C.V.} % Organization
{Villahermosa, Tabasco, MX} % Location
{Mar. 2016 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item{Collaboration on an ASP.Net MVC 5 app for calculating the daily oil \& gas distribution for PEMEX's exploration and production, with data retrieved from diverse institutional databases, including the data visualization for the each point of distribution network.}
	\item{Implementation the algorithm for the distribution calculation, including a task queue for running the algorithm without interrupting the web app.}
	\item{Development of the UI for the distribution network visualization, with Angular 1.5, Slickgrid, PDFjs and D3js {\tiny (see side-projects)}.}
	\item {Implementation of a battery of unit tests with Nunit for decreasing the validation time of the results from the distribution calculation, which also allowed to detect errors in the business logic due to bugs in the distribution network design.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Lead Front-end web developer \& .Net developer} % Job title
{Pemwork SAPI de C.V. - consulting to Compañía Mexicana de Exploraciones S.A. de C.V.} % Organization
{Villahermosa, Tabasco, MX} % Location
{Apr. 2015 - Mar. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item{Implementation}
\item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market. Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic, designed game graphics.}
\item {Won the 2nd prize in final evaluation.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Web developer \& .Net developer} % Job title
{Compañía Mexicana de Exploraciones S.A. de C.V.} % Organization
{Villahermosa, Tabasco, MX} % Location
{Jul. 2014 - Apr. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market. Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic, designed game graphics.}
		\item {Won the 2nd prize in final evaluation.}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{Web developer \& PHP/Android developer} % Job title
{Grupo Empresarial Syfors S.A. de C.V.} % Organization
{Saltillo, Coahuila, MX} % Location
{Sep. 2013 - May 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
	\item {Researched means of retrieving a corresponding video based on image contents using image similarity algorithm.}
	\item {Implemented prototype that users can obtain torrent magnet links of corresponding video relevant to an image on web site.}
	\end{cvitems} 
}

%------------------------------------------------

\cventry
{Freelance Web developer \& PHP/Python developer} % Job title
{Freelancer.com} % Organization
{Remote} % Location
{Jul. 2012 - Jun. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
	\item {Performed research memory management strategies of OS and implemented in Python an interactive simulator for Linux kernel memory management.}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{Graduate research in <Numerical simulation of Polymeric material synthesis>} % Job title
{Centro de Investigación en Química Aplicada} % Organization
{Saltillo, Coahuila, MX} % Location
{Apr. 2011 - Sep. 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
	\item {Developed a proxy drive smartphone application which connects proxy driver and customer. Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{Undergraduate intern} % Job title
{Centro de Desarrollo Tecnológico IDESA} % Organization
{Coatzacoalcos, Veracruz, MX} % Location
{Feb. 2009 - Jul. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
\item {Conducted penetration testing on SAMSUNG Smart TV.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}